---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidytab

> Create tidyverse-friendly tables of frequencies

<!-- badges: start -->
[![R-CMD-check](https://github.com/gvelasq/tidytab/actions/workflows/R-CMD-check.yaml/badge.svg?branch=main)](https://github.com/gvelasq/tidytab/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/gvelasq/tidytab/branch/main/graph/badge.svg)](https://codecov.io/gh/gvelasq/tidytab?branch=main)
[![CRAN status](https://www.r-pkg.org/badges/version/tidytab)](https://cran.r-project.org/package=tidytab)
[![R-universe status](https://gvelasq.r-universe.dev/badges/tidytab)](https://gvelasq.r-universe.dev/tidytab)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Installation

You can install tidytab from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("gvelasq/tidytab")
```

## Usage

```{r example, message = FALSE}
library(tidytab)

# one-way table of frequencies
mtcars |> tab(cyl)

# two-way table of frequencies (a special 2x2 contingency table)
mtcars |> tab(cyl, gear)

# flat contingency tables of three (or more) variables
mtcars |> tab(cyl, gear, am)

# tables wider than the R console are automatically wrapped
mtcars |> tab(cyl, gear, am, vs)

# missing values are displayed in red
tab(letters[24:27])

# ftab() displays only flat contingency tables (here, with two variables)
mtcars |> ftab(cyl, gear)

# tab1() displays one-way tables for each variable
mtcars |> tab1(cyl, gear)

# tab2() displays two-way tables for all variable combinations
mtcars |> tab2(cyl, gear, am)
```

## Code of Conduct

Please note that the tidytab project is released with a [Contributor Code of Conduct](https://gvelasq.github.io/tidytab/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## Contributors


<!-- ALL-CONTRIBUTORS-LIST:START - Do not remove or modify this section -->
<!-- prettier-ignore-start -->
<!-- markdownlint-disable -->

All contributions to this project are gratefully acknowledged using the [`allcontributors` package](https://github.com/ropensci/allcontributors) following the [all-contributors](https://allcontributors.org) specification. Contributions of any kind are welcome!

### Code

<table>

<tr>
<td align="center">
<a href="https://github.com/gvelasq">
<img src="https://avatars.githubusercontent.com/u/20712598?v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/gvelasq/tidytab/commits?author=gvelasq">gvelasq</a>
</td>
<td align="center">
<a href="https://github.com/askawron">
<img src="https://avatars.githubusercontent.com/u/128433085?v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/gvelasq/tidytab/commits?author=askawron">askawron</a>
</td>
<td align="center">
<a href="https://github.com/ramongss">
<img src="https://avatars.githubusercontent.com/u/47225177?v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/gvelasq/tidytab/commits?author=ramongss">ramongss</a>
</td>
</tr>

</table>


### Issue Authors

<table>

<tr>
<td align="center">
<a href="https://github.com/fkohrt">
<img src="https://avatars.githubusercontent.com/u/12914806?v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/gvelasq/tidytab/issues?q=is%3Aissue+author%3Afkohrt">fkohrt</a>
</td>
<td align="center">
<a href="https://github.com/zhizhongpu">
<img src="https://avatars.githubusercontent.com/u/84325421?u=762ebb2942d556c47b95a1840455edac00c75dd7&v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/gvelasq/tidytab/issues?q=is%3Aissue+author%3Azhizhongpu">zhizhongpu</a>
</td>
<td align="center">
<a href="https://github.com/theshiniss">
<img src="https://avatars.githubusercontent.com/u/122404801?u=3f42993ddd595afb03bd2acb2264bb08b55b0a9f&v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/gvelasq/tidytab/issues?q=is%3Aissue+author%3Atheshiniss">theshiniss</a>
</td>
</tr>

</table>


### Issue Contributors

<table>

<tr>
<td align="center">
<a href="https://github.com/lhdjung">
<img src="https://avatars.githubusercontent.com/u/71007825?u=d4103f66820f6a02c5838dda3aeb7e6b7dc8cb62&v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/gvelasq/tidytab/issues?q=is%3Aissue+commenter%3Alhdjung">lhdjung</a>
</td>
</tr>

</table>

<!-- markdownlint-enable -->
<!-- prettier-ignore-end -->
<!-- ALL-CONTRIBUTORS-LIST:END -->

